---
title: "Credit_Card_Customers"
output:
  word_document: default
  pdf_document: default
  html_document: default
date: "2023-01-27"
---
##Source: https://www.kaggle.com/datasets/sakshigoyal7/credit-card-customers

##import, View Print and Clean Dataset
```{r}
library("readr")
BankChurners<-read.csv("C:/Users/Chaur/OneDrive/Desktop/FML/BankChurners.csv/BankChurners.csv")

View(BankChurners)

Bank_data = subset(BankChurners,select = c(CLIENTNUM,Attrition_Flag,Customer_Age,Gender,Dependent_count,Education_Level,Marital_Status,Income_Category,Card_Category,Months_on_book,Total_Relationship_Count,Months_Inactive_12_mon,Contacts_Count_12_mon,Credit_Limit,Total_Revolving_Bal,Avg_Open_To_Buy,Total_Amt_Chng_Q4_Q1,Total_Trans_Amt,Total_Trans_Ct,Total_Ct_Chng_Q4_Q1,Avg_Utilization_Ratio))
```
##Structure of Dataset 
```{r}
str(Bank_data)
```
##Descriptive stastics
```{r}
summary(Bank_data)
```

## 98th Quantile, Interquantile, standard deviation and variance 
```{r}
quantile(Bank_data$Credit_Limit,0.98) ##98th Quantile of Credit_limit
IQR(Bank_data$Credit_Limit) ## the difference between First and 3rd Quantile
sd(Bank_data$Credit_Limit) ## standard deviation 
var(Bank_data$Credit_Limit) ## Variance
lapply(Bank_data[,15:21],sd)
lapply(Bank_data[,15:21],var)
```
##Transform Variables
#convert CLIENTNUM from integer into Character since its a Client ID
```{r}
Bank_data$Client_ID = as.character(Bank_data$CLIENTNUM)
class(Bank_data$Client_ID)
```

##Transform Variables
#Creating a New variable "Duration_in_Years" based on Months_on_Book
```{r}
library(dplyr)
names(Bank_data)
Bank_data_2 <- Bank_data %>%
mutate(Duration_in_year = case_when(Months_on_book < 13 ~ 'New Accounts',
Months_on_book < 37 ~ ' 3 Year Old',
Months_on_book < 61 ~ '3-5 year old', TRUE ~ '5+ years Old'))
names(Bank_data_2)
unique(Bank_data_2$Duration_in_year)
```
## Preparing Data for BarChart 
```{r}
bank_data_3 <- Bank_data_2 %>% group_by(Income_Category) %>%
summarise(avg_credit_limit = mean(Credit_Limit))
unique(Bank_data_2$Income_Category)
Bank_data_4 <- bank_data_3 %>%
mutate(Income_Category2 = recode(Income_Category, "Less than $40K" = 'A.<$40K',
"$40K - $60K" = 'B.$40K-$60K',
"$60K - $80K" = 'C.$60K-$80K', 
"$80K - $120K" = 'D.$80K-$120K',
"$120K +" = 'E.>$120K',
Unknown = 'F.Unknown'))
Bar_graph_data <- subset(Bank_data_4,select = c(Income_Category2,avg_credit_limit)) 
Bar_graph_data2 = Bar_graph_data[order(Bar_graph_data$Income_Category2),]
View(Bar_graph_data2)
````
## Barchart Credit limit Vs Income 
```{r}
main <- par(cex.axis = 0.5, cex.lab = 0.5,cex.sub =0.5, cex.main = 1)
barplot(Bar_graph_data2$avg_credit_limit,
main = " Credit Limit By Income",
xlab = "Income Category ($'000)", 
ylab = "Average Credit Limit",
ylim = c(0,20000),
names.arg = Bar_graph_data2$Income_Category2,
border = 'Red',
col = "Blue",
density = 10)
````
## Scatterplot between credit limit Vs Month on Book

```{r}
main <- par(cex.axis = 0.5, cex.lab = 0.5,cex.sub =0.5, cex.main = 1)
Scatter_graph = subset(Bank_data , select= c ("Months_on_book","Credit_Limit"))
Scatter_graph2 <- head(Scatter_graph, n =500)
View(Scatter_graph2)
X = Scatter_graph2$Months_on_book
Y = Scatter_graph2$Credit_Limit
plot(X,Y,  main = "Credit limit Vs MOB", 
     xlab = "Month on Books", ylab = "Credit Limit")
abline(lm(Y ~ X),col="Red")
````
```{r}
main <- par(cex.axis = 0.5, cex.lab = 0.5,cex.sub =0.5, cex.main = 1)
Scatter_graph = subset(Bank_data , select= c ("Total_Revolving_Bal","Credit_Limit"))
Scatter_graph2 <- head(Scatter_graph, n =500)
View(Scatter_graph2)
X = Scatter_graph2$Total_Revolving_Bal
Y = Scatter_graph2$Credit_Limit
plot(X,Y,  main = "Credit limit Vs R. Balance", 
     xlab = "Revolving Balance", ylab = "Credit Limit")
abline(lm(Y ~ X),col="Red")
````
```{r}
main <- par(cex.axis = 0.5, cex.lab = 0.5,cex.sub =0.5, cex.main = 1)
Scatter_graph = subset(Bank_data , select= c ("Customer_Age","Credit_Limit"))
Scatter_graph2 <- head(Scatter_graph, n =500)
View(Scatter_graph2)
X = Scatter_graph2$Customer_Age
Y = Scatter_graph2$Credit_Limit
plot(X,Y,  main = "Customer age Vs Credit limit", 
     xlab = "Customer Age", ylab = "Credit Limit")
abline(lm(Y ~ X),col="Red")
````